%====================================================
% Abstract Template (ENG)
% The 29th Annual Meeting in Mathematics (AMM2025)
% Srinakharinwirot University
%====================================================

\documentclass[12pt, a4paper]{article}
\usepackage{geometry,graphicx}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage[hidelinks]{hyperref}

\geometry{top=5cm, bottom=2.5cm, left=2.5cm, right=2.5cm, headheight=3cm}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newenvironment{AMM-abstract}[4][]{
  \begin{center}
    { \renewcommand\textsuperscript[1]{}\par}
    {{\Large\bfseries #2}\par}
    \medskip
    {\large #3\par}
    \bigskip
    {\small #4\par}
    \bigskip\bigskip
    {{\large\bfseries Abstract}\par}
  \end{center}
}{ 
  \bigskip
  \hrule
  \bigskip
}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}

\newcommand{\mykeywords}[1]{%
    \noindent \textbf{Keywords:} #1 \par
}
\newcommand{\myMSC}[1]{
    \noindent \textbf{2020 MSC:} #1 \par
}

\fancyhead[L]{\footnotesize
The 29\textsuperscript{th} Annual Meeting in Mathematics (AMM 2025)\\
Department of Mathematics, Faculty of Science,\\
Srinakharinwirot University,
Bangkok, Thailand}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% DO NOT make any changes above this line %%%%%
%%%%%% DO NOT use any customized definitions %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%% INSTRUCTION %%%%%%%%%%%%%%%%%%%%
% Use the following command to write your abstract:
%
% \begin{AMM-abstract}[]
% {Title}
% {Authors (use \textsuperscript as institution markers)}
% {Institutions (use \textsuperscript as institution markers)}
% Abstract text
% \end{AMM-abstract}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{AMM-abstract}[]
{Your Title Goes Here} %TITLE
{First Author\textsuperscript{1,}\footnote{Speaker (name@email.com)}, Second Author\textsuperscript{1}, and Third Author\textsuperscript{2,}\footnote{(Optional) The author is partially supported by ...}} %AUTHORS
{\textsuperscript{1}Department of Mathematics, Faculty of Science\\Srinakharinwirot University,
Bangkok 10110, Thailand\\ \smallskip
\textsuperscript{2}Department of Mathematics Statistics and Computer, Faculty of Science\\
Ubon Ratchathani University, Ubon Ratchathani 34190, Thailand} %AFFILIATIONS

%YOUR ABSTRACT GOES HERE
Write a concise and compelling abstract of no more than 250 words. Your abstract should pique the reader's interest and provide a clear overview of your research.
To achieve this, structure your abstract as follows:

1) Background: Briefly introduce the broader context of your research and clearly state the specific research question or problem you address.
 
2) Method: Outline the primary methods or techniques used to investigate your research question.
 
3) Result: Summarize the key findings of your study.
 
4) Conclusion: Present the main conclusions or interpretations drawn from your results.
 
Your abstract should accurately reflect the content of your full paper. Avoid making exaggerated claims or introducing results that will not be presented at the conference.

For more information about Mathematics Subject Classification system (2020 MSC), please visit \url{https://mathscinet.ams.org/msnhtml/msc2020.pdf}.
\end{AMM-abstract}

%%%%%%%%%%%%%%%%% Keywords and MSC %%%%%%%%%%%%%%%%%%%%%%

\mykeywords{keyword1, keyword2, keyword3} %Please include 3-5 keywords here. Use comma to separate items in the list.
\smallskip
\myMSC{nnXxx, nnXxx, nnXxx} %Please include MSC here. The first item is the primary MSC. Use comma to separate items in the list.

\end{document}